gradient_analysis

### 2020-11-20 gradient_analysis.Rmd
change filepath
label

read data and make species and environmental matrices
```{r}
data <- read_csv(here("data/weighted_prev_competence.csv"))

@@

PCA: Principal Component Analysis - a rotation-based ordination method
```{r}

pca_env_output <- princomp(env_mat, cor=T) # PCA
biplot(pca_env_output) # Generates a bi-plot with vectors
vec1 <- envfit(pca_env_output$score[,1:2], community_mat, permutations=0) 
plot(vec1, col="blue")

>>>>

read data and make species and environmental matrices
```{r}
data <- read_csv(here("data/weighted_prev_competence_111220.csv"))

@@

PCA: Principal Component Analysis - a rotation-based ordination method
```{r}
#Direct Gradient Analysis w/ PCA
pca_env_output <- princomp(env_mat, cor=T) # PCA
biplot(pca_env_output) # Generates a bi-plot with vectors
vec1 <- envfit(pca_env_output$score[,1:2], community_mat, permutations=0) 
plot(vec1, col="blue")
